---
title: "Plotly"
output: html_document
---

# Here are some plots 

today we're making interactive plots in plotly

When making new page, updating navigation bar (in index yml), and then rebuild the website

```{r}
library(tidyverse)
library(p8105.datasets)
library(plotly)
```

Do some initial data cleaning / subsetting 

```{r}
data(nyc_airbnb)

nyc_airbnb = 
  nyc_airbnb %>%  
  mutate(rating = review_scores_location / 2) %>% 
  select(
    neighbourhood_group, neighbourhood, rating, price, room_type, lat, long) %>% 
  filter(
    !is.na(rating), 
    neighbourhood_group == "Manhattan",
    room_type == "Entire home/apt",
    price %in% 100:500)
```

Using plotly

```{r}
nyc_airbnb %>% 
  plot_ly(
    x = ~lat, y = ~long, color = ~price,
    type = "scatter", mode = "markers", alpha = 0.5
  )
```

alpha does transparency 

I want to consider what text do i want to appear when i hover cursor ontop 

```{r}
nyc_airbnb %>% 
  mutate(text_label = str_c("Price: ", price)) %>% 
  plot_ly(
    x = ~lat, y = ~long, color = ~price, text = ~text_label,
    type = "scatter", mode = "markers", alpha = 0.5
  )
```

Added a new column called text_label where the input in that column is "Price ___" where it is a string and then you can put into the text when hovering 


```{r}
nyc_airbnb %>% 
  mutate(text_label = 
           str_c("Price: ", price, "\nNeighborhood ", neighbourhood_group)) %>% 
  plot_ly(
    x = ~lat, y = ~long, color = ~price, text = ~text_label,
    type = "scatter", mode = "markers", alpha = 0.5
  )
```

n\ allows it for to be in a new line Neighbourhood 

```{r}
nyc_airbnb |> 
  mutate(neighbourhood = fct_reorder(neighbourhood, price)) |> 
  plot_ly(y = ~price, color = ~neighbourhood, type = "box", colors = "viridis")
```

```{r}
nyc_airbnb |> 
  count(neighbourhood) |> 
  mutate(neighbourhood = fct_reorder(neighbourhood, n)) |> 
  plot_ly(x = ~neighbourhood, y = ~n, color = ~neighbourhood, type = "bar", colors = "viridis")
```



